THE HERA DISH III : MEASURING ELEMENT CHROMATICITY WITH REFLECTOMETRY.

### 2016-09-16 DishReflectometry/Paper1_v3.tex
Almost edited everything

    Performance of the HERA feed and the dish-feed assembly has been simulated by
    the em solver "High Frequency Structural Simulator(HFSS)" using the finite
    element method.  The simulated and measured return loss of the feed, both
    magnitude and phase are shown in the upper panel of the figure
    \ref{RL_mag_dish}. While the simulated return loss of the feed structure shows
    two resonant peaks around 120 and $160~MHz$, the feed resonance occur at
    slightly higher frequencies. Notable are the difference in the shape of the
    resonant peaks. While the simulated response shows very wide resonant peaks, as
    expected from this dipole structures, the measured return loss of the feed has
    a narrow peak around its low frequency resonance. This feature dominates the
    fall off rate in the delay response of the system bandpass. The delay response
    of the feed is shown in figure \ref{ds_feed_on_dish_trans}.

@@

    Lower panel of the figure \ref{RL_mag_dish} shows the measured return loss when
    the feed is suspended at the focal plane of the parabolic dish which is at $5m$
    from the dish vertex. The measured return loss is much more complex than what
    is found from the simulation. 
    %To estimate the delay spectrum of the dish-feed assembly i.e one single HERA element, this measurement is first corrected to map the response of the antenna from transmitting mode to receiving mode via equation \ref{zero_delay_correction}. The corrected measurement is then Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{corrected_response}. 
    Measurement bandwidth is kept much larger than the bandwidth of operation to
    achieve higher delay resolution. A number of systematic effects as well as
    mathematical artifacts that are critical to this measurement and their effects
    on the corresponding estimation of the delay spectrum are taken in to account
    in determination of the delay spectrum and described below.

@@

    During observation, each HERA element is connected to an active balun similar
    to the ones used in the PAPER antenna which provides greater than 10dB return
    loss of power at the feed output as is achieved in the measurement presented
    here.These baluns are under further design improvements aiming at 10 to 20dB
    better impedance match between the feed and the balun than the measurements
    presented here.  Our measurement is done using a vector network analyzer for
    which the active balun has been replaced by a passive balun.Given the antenna
    impedance and the 50 Ohm transmission line the measurements are done using the
    passive balun with a 4:1 impedance ratio. This measurements are conservative
    estimate  for both $\Gamma_{f}$ and $s_{11}$.\\ While measuring the return loss
    of the dish-feed assembly, the signal transmitted by the VNA is reflected first
    off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq9}. This
    essentially represents a mismatch in between the feed and the 50 Ohm
    transmission line. In delay domain, this appears at the zero delay bin. The
    zero delay response is identical whether or not the feed is suspended on the
    dish. Therefore, we measure this response by measuring the feed return loss
    alone while the feed is kept on the ground facing the sky. This results in feed
    return loss alone including the surrounding cage structure but excluding the
    dish response. While $\Gamma_{f}$ fraction of incident voltage is reflected off
    the feed, $1+\Gamma_{f}$ fraction of the voltage is transmitted. In receiving
    mode, upon initial incidence, $\Gamma_{f}$ fraction of voltage is reflected
    back in to the space while $1+\Gamma_{f}$ voltage enters the feed. In receiving
    mode, in delay domain, this appears at the zero delay bin.  The using the
    return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement
    $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq11} and
    the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.

@@

    Measurement equations shows the effects of multiple reflections of the sky
    signal between the feed and the dish. Any other reflections off the feed
    structure and/or any other part of the dish-feed assembly would appear at
    arbitrary delays. The estimated delay spectrum of the instrument is
    collectively contributed by all the reflections. Delay spectrum estimated from
    the return loss measurement of the feed alone,  provides the lowest limit of
    the delay spectrum of the instrument considering there is no multiple
    reflections in between the feed and the dish.  From figure
    \ref{ds_feed_on_dish_trans}, at lower delays, the reflections are dominated by
    the feed structure. Therefore, the delay spectrum in both the cases follow each
    other. Since the distance between the feed and the dish is 5 m, the roundtrip
    delay between the dish and the feed as about $30~ns$. Hence, the dish
    reflection is expected to manifest themselves at an integral multiple of
    $30~ns$. The diameter of the feed cavity is $172~cm$  that results in signal
    reflections every integral multiple of $\approx2.86~ns$. The combined effect of
    feed and the dish dominates the delay spectrum up to $\> 50nS$ after which the
    dish reflections starts to dominate and the two delay spectrum deviates from
    each other. With some manipulation of the equation \ref{eq10}, we can estimate
    the dish return loss $\Gamma_{d}$ and corresponding delay spectrum as shown in
    the figure \ref{dish_delay_spectrum}.

@@

    Another effect that spill over of the smooth foreground power at higher delays
    is the multiple reflection of the received signal between the feed output and
    the input of the analog backend and correlators. In our measurements, the feed
    output is connected to the VNA via a 50 feet long LMR 400 cable. This length
    correspond to a delay of $\approx 120~nS$ for the signals travelling through
    the cable. The delay spectrum of both feed and feed-dish assembly shows an
    enhanced feature at this delay indicating a reflection from the VNA input. We
    measure the VNA input reflections by disconnecting the feed and connecting an
    open load at the feed input of the cable. The measured return loss is shown in
    the figure \ref{fig:open_RL}. Since the electromagnetic wave travelling through
    a transmission line undergoes a $100\%$ reflections from an open ended
    transmission line, we compute the combined effect of the VNA input return loss
    along with the cable resistive loss from this measurement as shown in figure
    \ref{fig:open_RL}. This results an important system design criterion for HERA.
    The VNA input return loss is found to be at a level of $-14$ to $-30dB$ across
    the measurement band. This is consistent with the matched provided by the
    commercially available RF connectors that are commonly used. This manifests
    itself in a peak in the delay spectrum which is $50~dB$ above the measurement
    noise floor. The delays at which this effect becomes dominant depends on the
    length of the cable. Due to finite return loss at the input of the backends,
    this effect will be present in all the observations and thus would impact the
    instrument delay spectrum. However, its effect could be reduced below the level
    where the foreground  achieving a return loss at the backend input is greater
    than at least $-30~dB$.

    \begin{figure*}[ht]
    \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[angle=0, width=\linewidth]{plots/open_RL.png}
    \end{minipage}
    \hspace{0.1cm}
    \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/open_delay.png}
    \end{minipage}
    \caption{Left: Magnitude and phase of the return loss measured when the open load is connected at the feed input of the cable. Ideally, for an open load, the electromagnetic wave travelling through the transmission cable undergoes a $100\%$ reflections and magnitude of the return loss is $0dB$. However, due to the resistive loss in the cable, the a small part of the signal is dissipated in the cable resulting a smaller return loss.  Right: Delay spectrum of the open load that shows the multiple reflections at the VNA input. The delay spectrum of the feed and the feed-dish assembly is also plotted for comparison.}
    \label{fig:open_RL}       
    \end{figure*}

@@

    Estimation of the delay spectrum by taking the Fourier transform of the
    measured return loss is sensitive to the bandwidth of measurements. Since the
    measurements are done in the spectral domain, measurement between two
    frequencies is analogous to windowing the frequency domain data by a square
    window function. In the delay domain, Fourier transform of this would result in
    multiple side lobes at higher delays. Therefore, appropriate windowing of the
    data is  necessary prior to taking the Fourier transform of the measured data.
    Figure \ref{fig:window} shows the delay spectrum estimated from the measured
    data using a square window as well as Blackman Harris window. Windowing the
    data prior to Fourier transform significantly reduces the system response
    higher delays.

    \begin{figure}
    \centering
    \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/ds_window.png}
    \caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz. Green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window. The delay spectrum of the windowed data set shows significant reduction in the instrument response at higher delays.}
    \label{fig:window}
    \end{figure}

@@

  \subsection{Comparison with simulations:}
  \begin{figure}{H}
  \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/simulation_comparison2.png}
  \caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the limits of foreground simulation (Thyagarajan et al).}
   \label{fig:sim_em}
   \end{figure}
 \subsubsection{Electromagnetic simulation:}  
We compare the delay spectrum estimated from our measurements with the same derived from the return loss obtained from the HFSS simulations of the HERA element (figure \ref{fig:sim_em}). The simulation is in good agreement with the measurements up to about 80~ns after which the cable reflection starts to manifests. The dominant term in the expression of  return loss of the HERA element in
    receiving mode (equation \ref{eq11}) is the zero delay term $(1+\Gamma_{f})$. As
    mentioned earlier, the feed reflection coefficient $\Gamma_{a}$ shows two
    resonances in between 100-140~MHz and 160-200~MHz. While the one at high
    frequency is a wider peak, the low frequency resonance shows a sharp feature in
    frequency. This dominates the overall shape of the delay spectrum in figure
    \ref{fig:sim_em}.\\
  \subsubsection{Time domain simulation:}  
    We also compare our measurements with the time domain simulation presented in ~\cite{Ewall-Wice_et_al2016}. In this simulation, electromagnetic response of the HERA element is determined as a function of time using the commercial numerical simulation software Microwave Studio developed by Computer Simulation Technology. The simulation assumed a constant $125\Omega$ impedance at the dipole terminals. In reality, dipole impedance is function of frequency across the entire band. This results in deviation between the simulated delay response and the delay spectrum estimate of our measurements. \\
     \subsubsection{Foreground simulation:}  
    We also compare our measurement with the foreground simulation of~\citep{Thyagarajan_et_al2016} as shown in the first panel of figure \ref{ds_full_sub_band}. The shaded region of each panel shows the EoR to
    foreground power ratio required for detection of 21~cm power spectrum at those
    individual delays~\citep{Thyagarajan_et_al2016}. This ratio is computed by
    using the HFSS simulation of chromatic antenna beam and the sky models. Diffused sky foreground model is
    incorporated from~\citep{deolivieracosta_et_al2008} whereas the point source
    contribution is estimated by combining the NRAO VLA Sky Survey (NVSS) at
    1.42~GHz~\citep{Condon_1998}, Sydney University Molonglo sky Survey (SUMSS)
    ~\citep{Bock_et_al_1999}, \citep{Mauch_et_al_2003} at 843~MHz. The EoR signal
    is simulated by using 21cmFAST \citep{Messinger_et_al2011}. The model
    parameters used by~\cite{Thyagarajan_et_al2016} for the EoR signal simulation
    are : Virial temperature of minimum mass of dark matter halos that host
    ionizing sources, $T_{vir}^{min} = 2*10^4 K$, Ionising efficiency $\eta = 20$,
    Mean Free Path of UV photons $R_{mfp} = 15Mpc.$ For these model parameter
    values, the redshift of $50\%$ reionization is predicted to be at $z = 8.5$ at
    150MHz.  Ideally, the delay response of the smooth foreground is confined at
    lower delays whereas the same for the EoR signal is spread across the entire
    delay range. However, due to system chromaticity of the simulated response of
    the HERA element, foreground spills over the higher delays.
    ~\cite{Thyagarajan_et_al2016} computes the required attenuation of the
    foreground with respect to the EoR power available at that delay in order for a
    detection of the EoR signal at that delay mode. It is shown that for a given
    delay mode, the estimate of a lower $k_{\parallel}$ mode requires a higher
    attenuation compared to a higher $k_{\parallel}$ mode. (For details
    ~\cite{Thyagarajan_et_al2016}). \\
     This simulation also, however, does not incorporate the frequency dependent antenna impedance that 
     results in a frequency dependent return loss of power at the antenna terminal. Hence, the shaded region shows the most      
     stringent limits of  EoR to foreground power ratio and sets the upper most limit of the required system performance under the assumption of non-chromatic return loss.

@@

@@

    compares the estimated delay spectrum with em simulation of~\cite{deBoer_2016} at various subband.  Sub band delay spectra are wider compared to full

@@

    The shaded regions are however represents the EoR to Foreground power ratio simulated across the entire band.
    The HFSS simulation of chromatic antenna beam, as incorporated by \cite{Thyagarajan_et_al2016} varies smoothly  	across frequency resulting in no significant changes in this simulation at various sub bands.  
     HERA system performance conforms directly to the limits as posed by simulations, at frequencies $>160~MHz$. With the measured system response including the multiple reflections, the instrument would be able to probe the spatial modes of interest $k_{\parallel}>0.2$ with very little foreground bleeding $k_{\parallel} \approx 0.2$.

@@

    The inverse variance weighting method is a method of aggregating two or more
    random variable to minimize the variance in their weighted average. In our
    case, the measured visibility is contributed by EoR, foreground and
    instrumental noise. Hence, the estimate of any of the constituent signals would
    benefit from if the measured data is weighted by the covariance of the
    individual components. This is reflected in our choice of the matrix
    $E^{\alpha}$.  $E^{\alpha} = {1 \over 2} C^{-1} Q_{\alpha} C^{-1}$ represents a
    weighting of the data vector $\bold x$ by inverse of its covariance. This
    results in the smallest vertical error bar in the power spectrum estimate $\hat
    p_{\alpha}$ \citep{liu_tegmark2011}.  However, there is no definite way to know the
    covariance of individual signal components prior to estimating them. In
    practice, the total covariance matrix $C$ is computed from the measured
    visibilities. It is a sum of covariances of the foreground, instrumental noise
    and the EoR signals. The highest covariance is rendered by the signal which is
    correlated over various frequency channels at all frequencies such as
    foreground. Hence, weighting the measured visibility by the inverse of the
    covariance results in order of magnitude reduction of foreground power against
    the EoR signal. \\ 
    Combining the inverse covariance weighting formalism with the
    foreground simulation of \cite{Thyagarajan_et_al2016}, we derive a new limit on
    required foreground attenuation with respect to the EoR signal for
    power spectrum estimation using HERA measurements. The foreground model of
    \cite{Thyagarajan_et_al2016} as described in section \ref{subband} is adopted here. We use
    the reflectometry measurements, corrected for the antenna response in the
    receiving mode, to compute the visibilities (eq 13) for the given model of the
    foreground, the EoR and the system noise. These visibilities formed the complex
    data vector $\bold x$. We compute the covariance matrix $C$ from the simulated
    data. $\bold x$ is then multiplied by the inverse of the covariance matrix.
    This step essentially weighs down the foreground contribution to the measured
    data. Once Fourier transformed, the delay spectrum of the simulated data is
    constituted by linear super position of the delay spectrum of the foreground,
    the EoR signal.  We again compute the EoR to foreground power ratio which is
    now large due to relatively smaller foreground contribution than what is estimated in \cite{Thyagarajan_et_al2016} as shown       in fig: \ref{fig:sim_fg_revised}.

    \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/HERA_ds_fg_sim_rev.png}
    \caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyzer. The colored region shows the revised EoR to foreground power ratio in comparison to the measurements and the foreground simulation presented in \cite{Thyagarajan_et_al2016}.}
    \label{fig:sim_fg_revised}
    \end{figure*}
    This demonstrates that the performance of the HERA element, in conjunction with the inverse covariance method of foreground suppression, qualifies the system for its the science goal it is designed for, irrespective of its chromatic response generated due to multiple reflections in the system.

>>>>

    Return loss measurement of the HERA feed as well as dish-feed assembly is shown in figure \ref{RL_mag_dish}. Estimated        
    delay spectrum is shown in figure \ref{ds_feed_on_dish_trans}. A number of systematic effects as well as
    mathematical artifacts that are critical to this measurement and their effects
    on the corresponding estimation of the delay spectrum are discussed next.

@@

       %To estimate the delay spectrum of the dish-feed assembly i.e one single HERA element, this measurement is first corrected to map the response of the antenna from transmitting mode to receiving mode via equation \ref{zero_delay_correction}. The corrected measurement is then Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{corrected_response}. 
    %Measurement bandwidth is kept much larger than the bandwidth of operation to
    %achieve higher delay resolution.

@@

    During observation, each HERA element is connected to an active balun similar
    to the ones used in the PAPER antenna which provides greater than 10dB return
    loss of power at the feed output. These baluns are currently under further design 
    improvements aiming at 10 to 20dB
    better impedance match between the feed and the backend.
    Measurements presented here is done using a vector network analyzer for
    which the active balun has been replaced by a passive balun.Given the antenna
    impedance and the 50 Ohm transmission line the measurements are done using the
    passive balun with a 4:1 impedance ratio. This measurements are conservative
    estimate  for both $\Gamma_{f}$ and $s_{11}$.\\ While measuring the return loss
    of the dish-feed assembly, the signal transmitted by the VNA is reflected first
    off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq9}. This
    essentially represents a mismatch in between the feed and the 50 Ohm
    transmission line. In delay domain, this appears at the zero delay bin. The
    zero delay response is identical whether or not the feed is suspended on the
    dish. Therefore, we measure this response by measuring the feed return loss
    alone while the feed is kept on the ground facing the sky. This results in feed
    return loss alone including the surrounding cage structure but excluding the
    dish response. While $\Gamma_{f}$ fraction of incident voltage is reflected off
    the feed, $1+\Gamma_{f}$ fraction of the voltage is transmitted. In receiving
    mode, upon initial incidence, $\Gamma_{f}$ fraction of voltage is reflected
    back in to the space while $1+\Gamma_{f}$ voltage enters the feed. In receiving
    mode, in delay domain, this appears at the zero delay bin.  The using the
    return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement
    $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq11} and
    the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.

@@

    Measurement equations shows the effects of multiple reflections of the sky
    signal between the feed and the dish. Any other reflections off the feed
    structure and/or any other part of the dish-feed assembly would appear at
    arbitrary delays. The estimated delay spectrum of the instrument is
    collectively contributed by all the reflections. Delay spectrum estimated from
    the return loss measurement of the feed alone,  provides the lowest limit of
    the delay spectrum of the instrument considering there is no multiple
    reflections in between the feed and the dish.  From figure
    \ref{ds_feed_on_dish_trans}, at lower delays, the reflections are dominated by
    the feed structure. Therefore, the delay spectrum in both the cases follow each
    other. Since the distance between the feed and the dish is 5 m, the roundtrip
    delay between the dish and the feed as about $30~ns$. Hence, the dish
    reflection is expected to manifest themselves at an integral multiple of
    $30~ns$. The diameter of the feed cavity is $172~cm$  that results in signal
    reflections every integral multiple of $\approx2.86~ns$. The combined effect of
    feed and the dish dominates the delay spectrum up to $\> 50nS$ after which the
    dish reflections starts to dominate and the two delay spectrum deviates from
    each other. With some manipulation of the equation \ref{eq10}, we can estimate
    the dish return loss $\Gamma_{d}$ and corresponding delay spectrum as shown in
    figure \ref{dish_delay_spectrum}.

@@

    Another effect that spills over of the smooth foreground power at higher delays
    is the multiple reflection of the received signal between the feed output and
    the input of the analog backend and correlators. In our measurements, the feed
    output is connected to the VNA via a 50 feet long LMR 400 cable. This length
    corresponds to a delay of $\approx 120~nS$ for the signals traveling through
    the cable. The delay spectrum of both feed and feed-dish assembly shows an
    enhanced feature around this delay indicating a reflection from the VNA input. We
    measure the VNA input reflections by disconnecting the feed and connecting an
    open load at the feed input of the cable. The measured return loss is shown in
    figure \ref{fig:open_RL}. Since the electromagnetic wave traveling through
    a transmission line undergoes a $100\%$ reflections from an open ended
    transmission line, we compute the combined effect of the VNA input return loss
    along with the cable resistive loss from this measurement as shown in figure
    \ref{fig:open_RL}. This results an important system design criterion for HERA.
    The VNA input return loss is found to be at a level of $-14$ to $-30dB$ across
    the measurement band. This is consistent with the matched provided by the
    commercially available RF connectors that are commonly used. This manifests
    itself in a peak in the delay spectrum which is $50~dB$ above the measurement
    noise floor. The delays at which this effect becomes dominant depends on the
    length of the cable. Since our measurement plane is at the open end of the cable
    first reflection appears at zero delay while the second one appears around 120~ns. 
    Peak amplitude of the consecutive reflection is reduced by $22~dB$. Third and 
    consecutive reflections are buried in the noise floor of this measurement.Due to 
    finite return loss at the input of the backends,
    this effect will be present in all the observations and thus would impact the
    instrument delay spectrum. However, its effect could be reduced below the level
    where the foreground  achieving a return loss at the backend input is greater
    than at least $-30~dB$.

    \begin{figure*}[ht]
    \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[angle=0, width=\linewidth]{plots/open_RL.png}
    \end{minipage}
    \hspace{0.1cm}
    \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/open_delay.png}
    \end{minipage}
    \caption{Left: Magnitude and phase of the return loss measured when the open load is connected at the feed input of the cable. Ideally, for an open load, the electromagnetic wave traveling through the transmission cable undergoes a $100\%$ reflections and magnitude of the return loss is $0dB$. However, due to the resistive loss in the cable, the a small part of the signal is dissipated in the cable resulting a smaller return loss.  Right: Delay spectrum of the open load that shows the multiple reflections at the VNA input. The delay spectrum of the feed and the feed-dish assembly is also plotted for comparison.}
    \label{fig:open_RL}       
    \end{figure*}

@@

    Estimation of the delay spectrum by taking the Fourier transform of the
    measured return loss is sensitive to the bandwidth of measurements. Since the
    measurements are done in the spectral domain over finite bandwidth, it is analogous
     to windowing the frequency domain data by a square
    window function. In the delay domain, Fourier transform of this would result in
    multiple side lobes at higher delays. Appropriate windowing of the
    measured data is necessary prior to taking the Fourier transform reduces
    the system response at higher delays by few orders of magnitude~\citep{nithya_et_al2013}.
    Figure \ref{fig:window} shows the delay spectrum estimated from the measured
    data using a square window as well as Blackman Harris window. Even though windowing 
    results in about $50\%$ loss of spectral sensitivity, it provides an additional $30~dB$ headroom 
    for the foreground contaminations at higher delays. Spectral sensitivity could be improved by longer integration
    time.     
    \begin{figure}
    \centering
    \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/ds_window.png}
    \caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz. Green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window. The delay spectrum of the windowed data set shows significant reduction in the instrument response at higher delays.}
    \label{fig:window}
    \end{figure}

@@

  \subsection{Comparison with simulations:}
  \begin{figure}{H}
  \centering
  \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/simulation_comparison2.png}
  \caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the limits of foreground simulation (Thyagarajan et al).}
   \label{fig:sim_em}
   \end{figure}
 \subsubsection{Electromagnetic simulation:}  
 Performance of the HERA feed and the dish-feed assembly has been simulated by
    the em solver "High Frequency Structural Simulator(HFSS)" using the finite
    element method.  The simulated and measured return loss of the feed, both
    magnitude and phase are shown in the upper panel of figure
    \ref{RL_mag_dish}. Bottom panel of figure \ref{RL_mag_dish} shows the measured return loss when
    feed is suspended at the focal plane of the parabolic dish which is at $5m$
    from the dish vertex. The measured return loss is much more complex than what
    is found from simulation. 
    While the simulated return loss of the feed structure shows
    two resonant peaks around 120 and $160~MHz$, the feed resonance occur at
    slightly higher frequencies. Notable are the difference in the shape of the
    resonant peaks. While the simulated response shows very wide resonant peaks, as
    expected from these dipole structures, the measured return loss has
    a narrow peak at its low frequency resonance. The dominant term in the expression of  return loss of the HERA element in
    receiving mode (equation \ref{eq11}) is the zero delay term $(1+\Gamma_{f})$. Hence the low frequency peak dominates the overall shape of the delay spectrum in figure
    \ref{fig:sim_em}.\\

   \subsubsection{Time domain simulation:}  
    We also compare our measurements with the time domain simulation presented in ~\cite{Ewall-Wice_et_al2016}. In this simulation, electromagnetic response of the HERA element is determined as a function of time using the commercial numerical simulation software Microwave Studio developed by Computer Simulation Technology. The simulation assumed a constant $125\Omega$ impedance at the dipole terminals. In reality, dipole impedance is function of frequency across the entire band. This results in deviation between the simulated delay response and the delay spectrum estimate of our measurements. \\
     \subsubsection{Foreground simulation:}  
    We also compare our measurement with the foreground simulation of~\citep{Thyagarajan_et_al2016} as shown in the first panel of figure \ref{ds_full_sub_band}. The shaded region of each panel shows the EoR to
    foreground power ratio required for detection of 21~cm power spectrum at those
    individual delays. This ratio is computed by
    using the HFSS simulation of chromatic antenna beam and the sky models. Diffused sky foreground model is
    incorporated from~\citep{deolivieracosta_et_al2008} whereas the point source
    contribution is estimated by combining the NRAO VLA Sky Survey (NVSS) at
    1.42~GHz~\citep{Condon_1998}, Sydney University Molonglo sky Survey (SUMSS)
    ~\citep{Bock_et_al_1999}, \citep{Mauch_et_al_2003} at 843~MHz. The EoR signal
    is simulated by using 21cmFAST \citep{Messinger_et_al2011}. The model
    parameters used for the EoR signal simulation
    are : Virial temperature of minimum mass of dark matter halos that host
    ionizing sources, $T_{vir}^{min} = 2*10^4 K$, Ionising efficiency $\eta = 20$,
    Mean Free Path of UV photons $R_{mfp} = 15Mpc.$ For these model parameter
    values, the redshift of $50\%$ reionization is predicted to be at $z = 8.5$ at
    150MHz.  
    EoR to foreground power ratio shows that for a given
    delay mode, the estimate of a lower $k_{\parallel}$ mode requires a higher
    attenuation compared to a higher $k_{\parallel}$ mode. 
     This simulation also, however, does not incorporate the frequency dependent antenna impedance that 
     results in a frequency dependent return loss of power at the antenna terminal. Hence, the shaded region shows the most      
     stringent limits of  EoR to foreground power ratio and sets the upper most limit of the required system performance under the assumption of non-chromatic return loss.

@@

    \label{sub-band}

@@

    compares the delay spectrum estimate obtained em simulation of~\cite{deBoer_2016} at various subband.  Sub band delay spectra are wider compared to full

@@

    The shaded regions however represents the EoR to Foreground power ratio simulated across the entire band.
    The HFSS simulation of chromatic antenna beam varies smoothly across frequency resulting in no significant changes in this simulation at various sub bands.  
     HERA system performance conforms directly to the limits as posed by simulations, at frequencies $>160~MHz$. With the measured system response including the multiple reflections, the instrument would be able to probe the spatial modes of interest $k_{\parallel}>0.2$ with very little foreground bleeding around $k_{\parallel} \approx 0.2$.

@@

    The inverse variance weighting method is a method of aggregating two or more
    random variable to minimize the variance in their weighted average. In our
    case, the measured visibility is contributed by EoR, foreground and
    instrumental noise. Hence, the estimate of any of the constituent signals would
    benefit from if the measured data is weighted by the covariance of the
    individual components. This is reflected in our choice of the matrix
    $E^{\alpha}$.  $E^{\alpha} = {1 \over 2} C^{-1} Q_{\alpha} C^{-1}$ represents a
    weighting of the data vector $\bold x$ by inverse of its covariance. This
    results in the smallest vertical error bar in the power spectrum estimate $\hat
    p_{\alpha}$ \citep{liu_tegmark2011}.  However, there is no definite way to know the
    covariance of individual signal components prior to estimating them. In
    practice, the total covariance matrix $C$ is computed from the measured
    visibilities. It is a sum of covariances of the foreground, instrumental noise
    and the EoR signals. The highest covariance is rendered by the signal which is
    correlated over various frequency channels at all frequencies such as
    foreground. Hence, weighting the measured visibility by the inverse of the
    covariance results in order of magnitude reduction of foreground power against
    the EoR signal. \\ 
    Combining the inverse covariance weighting formalism with the
    foreground simulation of \cite{Thyagarajan_et_al2016}, we derive a new limit on
    foreground attenuation with respect to the EoR signal required for
    power spectrum estimation using HERA measurements. The foreground model of
    \cite{Thyagarajan_et_al2016} as described in section \ref{sub-band} is adopted here. We use
    the reflectometry measurements, corrected for the antenna response in the
    receiving mode, to compute the visibilities (eq 13) for the given model of the
    foreground, the EoR and the system noise. Notable here is, our measurement contains 
     beam chromaticity as well as chromaticity of the antenna impedance i.e, the effect 
     of return loss of power at the antenna terminal . These visibilities formed the complex
    data vector $\bold x$. We compute the covariance matrix $C$ from the simulated
    data. $\bold x$ is then multiplied by the inverse of the covariance matrix.
    This step essentially weighs down the foreground contribution to the measured
    data. Once Fourier transformed, the delay spectrum of the simulated data is
    constituted by linear super position of the delay spectrum of the foreground,
    the EoR signal.  We again compute the EoR to foreground power ratio which is
    now large due to relatively smaller foreground contribution than what is estimated in \cite{Thyagarajan_et_al2016} as shown       in fig: \ref{fig:sim_fg_revised}.

    \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/HERA_ds_fg_sim_rev.png}
    \caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyzer. The colored region shows the revised EoR to foreground power ratio in comparison to the measurements and the foreground simulation presented in \cite{Thyagarajan_et_al2016}.}
    \label{fig:sim_fg_revised}
    \end{figure*}
    This demonstrates that the performance of the HERA element, in conjunction with the inverse covariance method of foreground suppression, qualifies the system for its the science goal it is designed for, irrespective of its intrinsic chromatic response as well as chromaticity generated due to multiple reflections in the system.
